\sysfull

### 2017-08-10 paper/evaluation.tex
Made placeholders for figures in evaluation section

\vspace{2cm}

List of figures: 
\begin{itemize}
	\item Fig. 1: Viper only/per app/fixed power/(hand/complier)/no coalescing/clang [Resuls are ready by Kiwan]
	\item Fig. 2: Viper only/per app/per distance (fixed/20/40/60)/(hand/complier)/coalescing [Resuls are ready by Kiwan]
	\item Fig. 3a: (Viper Coalescing/Chain)/per app/per distance (fixed/20/40/60)/complier/clang [Resuls are ready by Kiwan]
	\item Fig. 3b: (Viper Coalescing/Chain)/per app/per distance (fixed/20/40/60)/complier/gcc [Resuls are not ready: Kiwan needs to make them]
	\item Fig. 4: exactly as Fig 12 in the paper (4 apps only)
	\item Fig. 5: average virtual task size/gcc/fixed distance/per app 
\end{itemize}

\vspace{2cm}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/virtualTaskSize.eps}
	\caption{Execution time of a dummy application containing twelve empty tasks as a function of coalescing factor. We observe three times improvement from coalescing until four virtual tasks, while we observe a diminishing return from task coalescing beyond four. \todo{Improve the figure: make it narrower, larger font, remove legend, do not capitalize "Task" in X axis, add Y axis label (Execution time (ms))}{Amjad}}
	\label{fig:virtualTaskSize}
\end{figure}

The question remains: does coalescing all program's tasks into a singe virtual task (as the energy becomes fully available, i.e. from energy harvesting to continuous power environment) is the best one? To answer this question we have implemented a simple program composed of $x$ empty tasks. We execute the same program by increasing coalescing factor by one while the device on which the program was executed was running on a stable power supply (refer to Section~\ref{sec:methodology_evaluation} for details). The result is presented in Figure~\ref{fig:virtualTaskSize}. We observe a significant increase in execution time as task are coalescent from one to four (three times execution time improvement). However, as the coalescing increases beyond four, we observe diminishing returns from coalescing in terms of execution time. \todo{Decide whether to place this figure in Evaluation section or leave it here}{Przemek}

@@

Expected results:
\begin{itemize}
	\item performance for each application comparing bars for Chain, no coalescing/hand-tasked, coalescing/hand-tasked, no-coalescing/compiler, coalescing/compiler. Performance depicted, normalized to one of the configurations (probably Chain). This plot will cover most of the eval dimensions that we care about.
	\item Sensitivity plot---show amount of task merged, time to completion, overhead (in terms of task-size/cap-size sweep (remember we can vary either with approximately the same effect)), energy consumed. All experiments for fixed power, at 3 distances with wireless power, compared against Chain for 3 task/cap size configurations
\end{itemize}

@@

\todo{Provide results and text to this section}{Amjad}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/chain_vipe}
	\caption{Time to complete for a set of testing applications (refer to Table~\ref{table:benchmark_list}) using \sys versus Chain (no coalescing applied, fixed power supply). \todo{Figure placeholder---will be replaced with final one}{Amjad}}
	\label{fig:IPOSPerformance}
\end{figure}

>>>>

%\vspace{2cm}

%List of figures: 
%\begin{itemize}
%	\item Fig. 1: Viper only/per app/fixed power/(hand/complier)/no coalescing/clang [Resuls are ready by Kiwan]
%	\item Fig. 2: Viper only/per app/per distance (fixed/20/40/60)/(hand/complier)/coalescing [Resuls are ready by Kiwan]
%	\item Fig. 3a: (Viper Coalescing/Chain)/per app/per distance (fixed/20/40/60)/complier/clang [Resuls are ready by Kiwan]
%	\item Fig. 3b: (Viper Coalescing/Chain)/per app/per distance (fixed/20/40/60)/complier/gcc [Resuls are not ready: Kiwan needs to make them]
%	\item Fig. 4: exactly as Fig 12 in the paper (4 apps only)
%	\item Fig. 5: average virtual task size/gcc/fixed distance/per app 
%\end{itemize}

%\vspace{2cm}

\subsubsection{\sys Performance}
\label{sec:result_coalescing}

@@

%\begin{figure}
%	\centering
%	\includegraphics[width=\columnwidth]{figures/virtualTaskSize.eps}
%	\caption{Execution time of a dummy application containing twelve empty tasks as a function of coalescing factor. We observe three times improvement from coalescing until four virtual tasks, while we observe a diminishing return from task coalescing beyond four. \todo{Improve the figure: make it narrower, larger font, remove legend, do not capitalize "Task" in X axis, add Y axis label (Execution time (ms))}{Amjad}}
%	\label{fig:virtualTaskSize}
%\end{figure}

%The question remains: does coalescing all program's tasks into a singe virtual task (as the energy becomes fully available, i.e. from energy harvesting to continuous power environment) is the best one? To answer this question we have implemented a simple program composed of $x$ empty tasks. We execute the same program by increasing coalescing factor by one while the device on which the program was executed was running on a stable power supply (refer to Section~\ref{sec:methodology_evaluation} for details). The result is presented in Figure~\ref{fig:virtualTaskSize}. We observe a significant increase in execution time as task are coalescent from one to four (three times execution time improvement). However, as the coalescing increases beyond four, we observe diminishing returns from coalescing in terms of execution time. \todo{Decide whether to place this figure in Evaluation section or leave it here}{Przemek}

\subsubsection{\sys Compiler Overhead}
\label{sec:result_compiler time}

\begin{figure}
	\centering
	%\includegraphics[width=\columnwidth]{figures/}
	\caption{\sys compiler overhead.}
	\label{fig:coalescing}
\end{figure}

\subsubsection{Virtual Task Size}
\label{sec:result_task_size}

@@

%\subsubsection{Completion Time}
%\label{sec:result_completion}

%\begin{figure}
%	\centering
%	\includegraphics[width=\columnwidth]{figures/chain_vipe}
%	\caption{Time to complete for a set of testing applications (refer to Table~\ref{table:benchmark_list}) using \sys versus Chain (no coalescing applied, fixed power supply). \todo{Figure placeholder---will be replaced with final one}{Amjad}}
%	\label{fig:IPOSPerformance}
%\end{figure}

%Expected results:
%\begin{itemize}
%	\item performance for each application comparing bars for Chain, no coalescing/hand-tasked, coalescing/hand-tasked, no-coalescing/compiler, coalescing/compiler. Performance depicted, normalized to one of the configurations (probably Chain). This plot will cover most of the eval dimensions that we care about.
%	\item Sensitivity plot---show amount of task merged, time to completion, overhead (in terms of task-size/cap-size sweep (remember we can vary either with approximately the same effect)), energy consumed. All experiments for fixed power, at 3 distances with wireless power, compared against Chain for 3 task/cap size configurations
%\end{itemize}

@@

%\todo{Provide results and text to this section}{Amjad}

@@
